*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
- more de-camelcasing of non-exported functions; - cull "::" calls; - make "devtools" suggested; - increment version further;

```{r, echo = FALSE}
max_PPR <- read.delim(
    file.path(tmpDir,"inputTable.txt"),
    check.names = FALSE) %>%
  flippant:::calculatePpr() %>%
  max(
    na.rm = TRUE) %>%
  signif(
    digits = 2
  )
```

>>>>

```{r, echo = FALSE}
max_PPR <- read.delim(
    file.path(tmpDir,"inputTable.txt"),
    check.names = FALSE) %>%
  flippant:::calculate_ppr() %>%
  max(
    na.rm = TRUE) %>%
  signif(
    digits = 2
  )
```
